---
title: "Probability Integral Transformation"
output:
  html_document: default
---

### PDF and CDF:  

\begin{equation}
  MD_G(y) = 1/[1+(y-\mu_G)'\Sigma_G^-1(y-\mu_G) ]
\end{equation}

\begin{equation}
Y \sim BN(\mu=
    \begin{bmatrix}
      0 \\
      0
    \end{bmatrix},
    \sigma^2 =  
    \begin{bmatrix}
      1 & 0\\
      0 & 1
    \end{bmatrix})
\end{equation}


\begin{equation}
M = \frac{(\vec{y}^T)
    \begin{bmatrix}
      1 & 0\\
      0 & 1
    \end{bmatrix}
  (\vec{y})
}{\sigma^2} \sim x^2(2) = exp(\lambda=0.5)
\end{equation}


\begin{equation}
  f(m) = 0.5e^{-0.5m},\quad m>0
\end{equation}


\begin{equation}
  N = \frac{1}{1+M},\quad 0<N<1
\end{equation}

\begin{equation}
  F_{N}(n) =P(N\leq n) = P( \frac{1}{1+M}\leq n ) = P(M \geq\frac{1}{n}-1)
  \\= \int_{\frac{1}{n}-1}^\infty 0.5e^{-0.5m}dm
  \\= exp(\frac{n-1}{2n}),\quad 0<n<1
\end{equation}

<div class="hightlight">
> \begin{equation}
>  f(n) =\frac{1}{2n^2}exp(\frac{n-1}{2n}),\quad 0<n<1
>\end{equation}
><br>
>
>\begin{equation}
>  F(n)= exp(\frac{n-1}{2n})
>\end{equation}

</div>

```{r,warning=F}
library(magrittr)
library(ggplot2)
set.seed(8+9)
pdf = function(x){1/(2*x^2)*exp((x-1)/(2*x))}
cdf = function(x){exp((x-1)/(2*x))}

ggplot(data.frame(x=c(0, 1)), aes(x)) + 
  stat_function(fun=pdf,color ="lightblue3",size=1) + 
  labs(title="pdf")
ggplot(data.frame(x=c(0, 1)), aes(x)) + 
  stat_function(fun=cdf,color ="lightpink2",size=1) + 
  labs(title="cdf")  

```  

Now, try to simulate samples by prob. integral trnasformation:

1. find $F^{-1}(y)$ 

\begin{equation}
  Y =  F(n)= exp(\frac{n-1}{2n}) \sim Unif(0,1)
  \\F^{-1}(y) = \frac{1}{1-2ln(Y)} \quad ,0<Y<1

\end{equation}

<div class= "blue">
```{r}
CDF_inverse = function(y){
   1/(1-2*log(y))
}
```  
</div>

2. Create samples by $Unif(0,1)$ 

```{r}
sample = sapply(runif(1000,0,1),CDF_inverse)
sample %>% summary()
  
```  


3. comparison cdf with empirical distribution function 
```{r,warning=F}
ggplot(data.frame(x=sample,g = as.factor(base::rep("sample",1000))),aes(x,color=g)) +
  geom_density(adjust = 0.8,size=1) +
  stat_function(data = data.frame(x=c(0,1)),aes(x,color="pdf"),
                fun=pdf,size=1) 

```   



